### 2022-04-26 README.Rmd
structure of biclar readme
populate with some details

---
output: github_document
---

@@

# bicla-R

<!-- badges: start -->
<!-- badges: end -->

The goal of bicla-R is to store code and (in the releases) data for estimating cycling potential and influencing policy.

@@

- TRIPS_original.Rds, the original OD dataset

@@

>>>>

---
output: github_document
bibliography: refs.bib
---

@@

# biclar

<!-- badges: start -->

<!-- badges: end -->

The goal of `biclar` is to store code and (in the releases) data for estimating cycling potential and influencing policy.

**biclar** is a tool for the design and assessment of different scenarios of the cycling network models in the Lisbon metropolitan area (LMA).

@@

-   Trips dataset with Origin and Destination, at *Freguesia* level, disaggregated by transport mode, from @IMOB  
-   [CAOP 2020](https://www.dgterritorio.gov.pt/cartografia/cartografia-tematica/caop?language=en) - Official limits of Portuguese areas.
-   Road network from [OpenStreetMap](https://www.openstreetmap.org/#map=11/38.7053/-9.1585)  
-   Main public transport interfaces at Lisbon Metro Region, provided by [Transportes Metropolitanos de Lisboa](https://www.tmlmobilidade.pt/)

<!-- todo: include shape of transport hubs in releases -->

# Cenarios for cycling uptake

## Baseline

The baseline scenario makes use of the 2018 mobility survey data in LMA.  
We considered all trips between _Freguesias_.

<!-- todo: include map of baseline scenario -->

See vignette [baseline scenario]() to see how this was modeled.

## ENMAC targets

The National targets for cycling uptake were set to:

-   4% of all trips should be made by bicycle by 2025
-   10% of all trips should be made by bicycle by 2030

Cycling trips should replace car trips directly.

See vignette [ENMAC scenario]() to see how this was modeled.

## Intermodal trips

See vignette [Intermodal scenario]() to see how this was modeled.

## E-bikes investment policy

See vignette [E-bike scenario]() to see how this was modeled.

# Methods

## PCT - Propensity to Cycle Tool

`biclar` uses the methods developed in [PCT.bike](https://pct.bike) [@Lovelace2017] for cycling uptake estimation and data visualization.

## Jittering

For the disagregation of OD pairs at _Freguesias_ level, we use [OD Jittering](https://github.com/atumworld/odrust) [@Jittering2022] method, which better suits walking and cycling trips modelling (shorter distances), instead of relying on centroids that concentrate all the trips between areas.

@@

## Cycling routes

Use of [CyclingStreets.net](https://cyclinstreets.net) ([R package](https://rpackage.cyclestreets.net/)) for fast and quiet bike routes for baseline scenario.  
For e-bike scenario, we developed a proper algorithm, considering the topography (and [`slopes`](https://docs.ropensci.org/slopes) package).

## Intermodal trips

We made use and developed a methodology that considers replacing long trips by bike + train or ferry trips (`name of the package`)

<!-- todo: include Robin's reflection about multi-modal trips replacement -->

## Estimation of socioeconomic benefits

Health Economic Assessment Tool ([HEAT v5.0](https://www.heatwalkingcycling.org/#how_heat_works)) for walking and cycling by WHO.

# Results

## Cycling uptake in LMA and by Municipality

## Comparision with the cycling network plans by Municipality

# References {-}
